MCC Predictions

### 2018-06-29 stats/ex3_comparisons.Rmd
fixing bug in exp 3 novel med and weak

@@

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.rsa.regPrior,
  llh.prior.regPrior,
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

>>>>

```{r model no prior loglikelihood}
no.prior.loglikelihood <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

   var conditionSpecificPriors = [.5, .5, .5]

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)

@@

llh.no.prior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, no.prior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "No Prior")

@@

likelihood_overview <- bind_rows(
  llh.no.prior,
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.rsa.regPrior,
  llh.prior.regPrior,
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)
